---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ARFAN

ARFAN (Analytical R Functions for Article Networks) is a comprehensive, elegant, and user-friendly R package designed for modern bibliometric and scientometric analysis.

Bridging the gap between raw citation data (from Scopus, Web of Science, PubMed, etc.) and publication-ready visualizations, ARFAN provides researchers with automated tools to map scientific literature, discover research gaps, and visualize academic networks.

✨ Key Features (In Development):
1. Executive Dashboards: Generate "One-Page" infographic summaries of your entire dataset.
2. Trend Analysis: Track publication growth, citations, and topic evolution over time.
3. Regional Analysis: Map global collaborations and country-specific research output.
4. Network Mapping: Visualize co-authorship, bibliographic coupling, and citation hubs.
5. Text Mining: Generate beautiful word clouds and keyword co-occurrence networks.

## Authors / Contributors

* **Muhammad Almanfaluthi** - *Creator & Lead Developer* - [Almanfaluthi](https://github.com/Almanfaluthi)
* **Khusnul Fathoni Effendy** - *Methodology & Co-Author*
* **Satini Yuniarsih** - *Methodology & Co-Author*
* **Stefani Widodo** - *Methodology & Co-Author*
* **Zuhrotun Ulya** - *Methodology & Co-Author*
* **Shalahuddin Maulidi** - *Methodology & Co-Author*
* **Rara Tarika** - *Methodology & Co-Author*
* **Abidah Safitri** - *Methodology & Co-Author*

## Installation

You can install the development version of ARFAN like so:
"devtools::install_github("Almanfaluthi/ARFAN")"


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ARFAN)
alman_bib_A0_ExecutiveSummary(df_patientsafety)
alman_bib_A0_ExecutiveSummary(df_herbal_leptospirosis, primary_col = "#2c3e50", accent_col = "#e74c3c")
alman_bib_A0_ExecutiveSummary(df_herbal_snakebite, primary_col = "red", accent_col = "blue")
alman_bib_A0_ExecutiveSummaryIndo(df_herbal_tb, primary_col = "#1a5276", accent_col = "#e67e22")
alman_bib_A0_ExecutiveSummaryIndo(df_herbal_filaria, primary_col = "#2c3e50", accent_col = "#e74c3c")
```
