---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ARFAN

ARFAN (Analytical R Functions for Article Networks) is a comprehensive, elegant, and user-friendly R package designed for modern bibliometric and scientometric analysis.

Bridging the gap between raw citation data (from Scopus, Web of Science, PubMed, etc.) and publication-ready visualizations, ARFAN provides researchers with automated tools to map scientific literature, discover research gaps, and visualize academic networks.

✨ Key Features (In Development):
1. Executive Dashboards: Generate "One-Page" infographic summaries of your entire dataset.
2. Trend Analysis: Track publication growth, citations, and topic evolution over time.
3. Regional Analysis: Map global collaborations and country-specific research output.
4. Network Mapping: Visualize co-authorship, bibliographic coupling, and citation hubs.
5. Text Mining: Generate beautiful word clouds and keyword co-occurrence networks.

## Authors / Contributors

* **Muhammad Almanfaluthi** - *Creator & Lead Developer* - [Almanfaluthi](https://github.com/Almanfaluthi) - Department of Tropical Medicine and Parasitology, Faculty of Medicine, Universitas Muhammadiyah Purwokerto, Central Java, Indonesia
* **Khusnul Fathoni Effendy** - *Methodology & Co-Author* -  Faculty of Medicine, Brawijaya University, East Java, Indonesia
* **Satini Yuniarsih** - *Methodology & Co-Author* -  Muslim Kaffah Foundation, East Java, Indonesia
* **Stefani Widodo** - *Methodology & Co-Author* - Department of Public Health, Faculty of Medicine, Universitas Muhammadiyah Purwokerto, Central Java, Indonesia
* **Zuhrotun Ulya** - *Methodology & Co-Author*  -  Faculty of Medicine, Brawijaya University, East Java, Indonesia
* **Shalahuddin Maulidi** - *Methodology & Co-Author* - Lembaga Kesehatan Gigi dan Mulut Pusat Kesehatan TNI Angkatan Darat (Indonesian Army)
* **Rara Tarika** - *Methodology & Co-Author*  - Lembaga Kesehatan Gigi dan Mulut Pusat Kesehatan TNI Angkatan Darat (Indonesian Army)
* **Abidah Safitri** - *Methodology & Co-Author* -  Muslim Kaffah Foundation, East Java, Indonesia

## Installation

You can install the development version of ARFAN like so:
"devtools::install_github("Almanfaluthi/ARFAN")"


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ARFAN)
# Almanfaluthi et all (Evolution of Artificial Intelligence in Patient Safety Across South East Asia)
# https://doi.org/10.53806/iamsph.v7i1.1447
alman_bib_A0_ExecutiveSummary(df_patientsafety) 

# Arista Elda Monica et all (Herbal Medicine field in Tropical Disease Filariasis)
# https://doi.org/10.1051/bioconf/202515403002
alman_bib_A0_ExecutiveSummaryIndo(df_herbal_filaria, primary_col = "#2c3e50", accent_col = "#e74c3c")

# Ade Dian Shah Putri et all (Herbal Medicine field in Tropical Disease Leptospirosis)
# https://doi.org/10.1051/bioconf/202515404001
alman_bib_A1_TrendAnalysis(df_herbal_leptospirosis)

# Ilham Jaluludin et all (Herbal Medicine field in Tropical Disease Snake bite)
# https://doi.org/10.1051/bioconf/202515403005
alman_bib_A2a_AuthorsAnalysis(df_herbal_snakebite)

# Ilham Jaluludin et all (Herbal Medicine field in Tropical Disease Snake bite)
# https://doi.org/10.1051/bioconf/202515403005
alman_bib_A3a_GlobalHeatmap(df_herbal_snakebite)

# Ade Dian Shah Putri et all (Herbal Medicine field in Tropical Disease Leptospirosis)
# https://doi.org/10.1051/bioconf/202515404001
alman_bib_A3b_RegionalHeatmap(df_herbal_leptospirosis)

# Almanfaluthi et all (Evolution of Artificial Intelligence in Patient Safety Across South East Asia)
# https://doi.org/10.53806/iamsph.v7i1.1447
alman_bib_A4a_ProductivityCountry(df_patientsafety)

# Annisa Nur Azizah et all (Herbal Medicine field in Tropical Disease Tuberculosis)
# https://doi.org/10.1051/bioconf/202515403001
alman_bib_A4b_ProductivityInstitution(df_herbal_tb)

# Berlianda Nur Sabilla et all (Herbal Medicine field in Tropical Disease Dengue)
# https://doi.org/10.1051/bioconf/202515403003
alman_bib_A4c_ProductivityJournal(df_herbal_dengue)

# Berlianda Nur Sabilla et all (Herbal Medicine field in Tropical Disease Dengue)
# https://doi.org/10.1051/bioconf/202515403003
alman_bib_A5a_Keyword_Occurance(df_herbal_dengue)

# Annisa Nur Azizah et all (Herbal Medicine field in Tropical Disease Tuberculosis)
# https://doi.org/10.1051/bioconf/202515403001
alman_bib_A5b_Keyword_Cloud(df_herbal_tb)

# Almanfaluthi et all (Evolution of Artificial Intelligence in Patient Safety Across South East Asia)
# https://doi.org/10.53806/iamsph.v7i1.1447
alman_bib_A5c_Keyword_Trend(df_patientsafety)
```
